Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-30 Response/Response 2/response-1.tex

\cmnt{2} \review{In convergence proof (48), why does the 2nd inequality hold? In fact, to prove the feasibility of  \eqn{{m_{k+1}^{(i)}, w_{*}^{(i-1)};m_k^{(i)} }}, the part between 2nd and 3rd inequality is not necessary, \eqn{\leq 0} directly follows the 2nd inequality since the solution \eqn{m_{k+1}^{(i)}, \gamma_{k+1}^{(i)} } is the optimal solution, and therefore feasible.  }

\resp We have removed the additional inequality relating the previous operating point from (49) in the revised manuscript.

\cmnt{3} \review{The solutions SCA iterations \eqn{\mbf{m}^{(i)}_k} does not necessarily converge. In fact \eqn{\mbf{m}} has compact feasible region, and thus \eqn{\mbf{m}^{(i)}_k} has limit points for any specific \eqn{i}.  However \eqn{m_{*}^{(i)}} does not necessarily exist (the whole sequence \eqn{\mbf{m}^{(i)}_k} may be not convergent). Similar problem happens to \eqn{\mbf{w}^{(i)}_k}. }

\resp  Even though the objective converges in each \ac{SCA} update, it is not guaranteed for the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge. It follows from the convexity of the objective in problem (16), which can have multiple solutions in the feasible set. However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [30] and [31]. This approach ensures the uniqueness of the solution in each \ac{SCA} update.

Since our problem is (highly) nonconvex, there are possibly many stationary points. If we start from different initial points, we may end up in different stationary points. That is to say, the limit point of the \ac{SCA} approach is not unique. However, by regularizing the objective with a small quadratic term, the iterate in each step of the \ac{SCA} algorithm is unique. This and the fact that the set is compact ensure that the \ac{SCA} converges to a limit point. We have updated the manuscript to include this information in the convergence proof of the centralized algorithm in Appendix A. The above modifications are included in Appendix A-B around (46) and in Appendix A-C after (50).

### 2015-07-30 Response/Response 2/response-2.tex

	We remark that the choice of a sub-channel ordering scheme should also consider the number of backlogged packets associated with each user. We have emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user. We do not include in the manuscript due to space limitations, we have included in the response letter to answer the reviewers' question. We considered a system with \eqn{N = 4} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users. The \ac{PL} is distributed uniformly over \eqn{[0,-3]} dB. The number of backlogged packets assumed for each user is provided in the corresponding captions in Figure \ref{fig-review-1}.
	\begin{figure*}[h!]
		\centering
		\subfloat[][Number of backlogged packets for each user in bits \eqn{Q_k = [11,8,14,6,6,2,10,10,5,6,9,5]}]{
			\includegraphics[width=0.8\textwidth]{reviewer_2_Q1B.eps}
			\label{fig-review-1a}
		}
		\hfill
		\subfloat[][Number of backlogged packets for each user in bits \eqn{Q_k = [8,9,12,8,12,5,4,10,8,5,7,9]}]{
			\includegraphics[width=0.8\textwidth]{reviewer_2_Q1A.eps}
			\label{fig-review-1b}
		}
		\caption{Convergence of the algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace} using \me{\ell_1} norm}
		\label{fig-review-1}
	\end{figure*}

	Figure \ref{fig-review-1} compares different sub-channel ordering schemes in terms of the total number of backlogged packets remaining in the system. As can be seen from Figure \ref{fig-review-1}\subref{fig-review-1a}, the greedy sub-channel ordering provides a favorable way of choosing sub-channels to minimize the total number of backlogged packets. However in Figure \ref{fig-review-1}\subref{fig-review-1b}, it is evident that the greedy sub-channel ordering is no longer better in comparison to the few other random ordering schemes. We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic method under Section III-D final paragraph. However, it is worth noting that as the number of users in the system increases, all sub-channel ordering schemes are similar in minimizing the total number of backlogged packets in the system without any noticeable gain.

@@

	\vspace{1eM}
	[R2] Changxin Shi, Berry R.A., Honig M.L., ``{Bi-Directional Training for Adaptive Beamforming and Power Control in Interference Networks}," \textit{IEEE Transactions on Signal Processing}, vol.62, no.3, pp.607,618, Feb.1, 2014

	[R3] P. Jayasinghe, A. T\"{o}lli, J. Kaleva,  M. Latva-aho, "{Bi-directional Signaling for Dynamic TDD with Decentralized Beamforming}'', in \textit{Proceedings of IEEE ICC SmallNets Workshop}, London, UK, June, 2015		
	\vspace{1eM}

\cmnt{3} \review{If the authors can't prove the convergence of the ADMM algorithm (or the decomposition approach via KKT conditions) in Section IV.B, then at least, you should discuss the property of the fixed point of the algorithm. For example, does there exist a fixed point of the algorithm? If so, is the fixed point of the algorithm unique? Is any fixed point of the algorithm also the optimal solution of the original problem in (20)? Assuming that the ADMM algorithm converges to a fixed point, will the interference vector in (39) converges to the actual interference in the network? These questions must be clarified in the paper. Otherwise, it is not clear how the ADMM algorithm is related to the original problem in (20). Similar questions should also be answered for the decomposition approach via KKT conditions. }

\resp We thank the reviewer for raising the concern regarding the convergence of the distributed algorithms. We have substantially improved the clarity of both primal and the \ac{ADMM} based approach in the revised manuscript (see Appendix B). There, we have utilized the strong convexity of the objective function to ensure the uniqueness of the minimizer in each \ac{SCA} step. Additionally, since each subproblem in (20) or (28) has a convex feasible set, the convergence of the \ac{ADMM} scheme is guaranteed by using [10] and [36, Prop. 4.2] as discussed in Appendix B.

In our paper, the number of \ac{ADMM} iterations is denoted by \eqn{J_{\max}} in Algorithm 2. In order to obtain the centralized solution, we need to perform the distributed approaches until convergence or for very large value of \eqn{J_{\max}}. In practice, it may not be possible to perform the distributed methods until convergence. In such cases, the overall convergence of the objective sequence and beamformer iterates of Algorithm 2 is not guaranteed. The reason is that the strict monotonicity of the objective is not ensured in each \ac{SCA} update.

However, if we perform the distributed algorithms for significantly enough to ensure strict monotonicity of the objective, then the overall of convergence of Algorithm 2 is guaranteed by following the arguments in [27]. Note that in addition, uniqueness of the limit point is also necessary for the sequence convergence. It can be assured by regularizing the original convex objective with a quadratic term as in (46b) in each \ac{SCA} step to guarantee strong convexity, and thereby ensuring a unique minimizer and limit point.

Additionally, to reduce the signaling overhead involved with the information exchange due to multiple loops, we can also combine the \ac{MMSE} receiver update in (23b) after each \ac{SCA} step for the transmit precoders. If in addition \eqn{J_{\max}} is sufficiently large, then the strict monotonicity of the objective sequence is still ensured by the combined update. It follows from the fact that the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained after each \ac{SCA} update. The newly found solution is also feasible and the objective improves monotonically in strict sense. Therefore, if the above conditions are satisfied, then the convergence of the sequence of iterates is guaranteed.

For our simulation scenario, we have fixed the maximum number of \ac{ADMM} iterations in each \ac{SCA} step as \eqn{J_{\max} = 20}. Note that it is sufficient to ensure strict monotonic decrease of the objective value in each \ac{SCA} step. However, the number of iterations to ensure strict monotonicity of the objective depends on the problem under consideration. The practical significance of limited number of \ac{ADMM} iterations is discussed briefly in [10, Section 3.2.2].

Response for the reviewer questions related to the \ac{ADMM} convergence for subproblem (20).

\begin{itemize}
\item Note that the objective is regularized with a quadratic term to ensure strong convexity as discussed in [30], [31]. Since the primal objective and the augmented Lagrangian are strongly convex, the optimal solution is unique due to the convexity of the feasible domain. Therefore, the limit point of the \ac{ADMM} algorithm is unique, which guarantees the existence of fixed point.

\item Note that if the objective function is convex, then it can have multiple optimal solutions. However, due to the additional quadratic term in the objective of (20) in each \ac{SCA} step, uniqueness of the minimizer is ensured. Therefore, even though the original problem (20) with the convex objective has a set of fixed points, due to the strong convexity of the modified objective, the \ac{ADMM} will find a fixed point upon convergence. However, note that the choice of fixed point depends on the \ac{SCA} operating point, since it is also used to regularize the objective as in (46b).

\item Using the earlier argument, any fixed point is a solution for the problem (20), since the original convex objective can have multiple solutions. The particular choice of the fixed point of the \ac{ADMM} approach depends on the operating point used in the regularization term in the objective.

\item Upon convergence of the \ac{ADMM} approach, the interference vector is guaranteed to be equal to the actual interference seen in the network. This is the main principle of \ac{ADMM} where the local variables (the vectors in (38)) converge to the global variables, which are the actual inference vectors.

@@

\end{itemize}

On the other hand, the iterative method described in Algorithm 3 is based on a heuristic iterative approach to find a solution of \ac{KKT} equations, we cannot prove its convergence. When Algorithm 3 terminates, we will use the transmit and receive beamforming vectors to calculate the original objective. Based on the reviewer comments, we have mentioned that the convergence of the Algorithm 3 cannot be proved theoretically (see Appendix B last paragraph).

We have updated the manuscript to clarify all the points mentioned above. Please refer to Section IV-B last paragraph after (40) in the revised manuscript. Additional information regarding the convergence of the distributed algorithms is provided in Appendix B second paragraph. The discussion on the convergence of the KKT based approach for MSE reformulation scheme is also presented in Appendix B last paragraph. For reference purpose, we have also referred the interested reader to [10], which discusses exclusively about the \ac{ADMM} approach.

### 2015-07-30 Response/Response 2/response-3.tex

\review{The authors have introduced changes in the manuscript that improved the paper's quality. Additionally, the authors have taken into account the reviewers' comments giving clarifications and modifying the content when required. More specifically, the following aspects have been treated:}

\vspace{1eM}
\underline{\textit{Reply:}} We thank the reviewer for recognizing the changes made on our earlier manuscript. We also thank the reviewer for providing constructive comments to help us to improve our manuscript.

\begin{enumerate}
\cmnt{1} \review{Convexity of problem (16). The paragraphs surrounding (16) allow a better understanding of the usage of the additional variables, i.e. gamma and beta, to remove the equality constraint in (2). For the reviewer remains however unclear, the procedure/criterion to determine the operating point for the parameter \eqn{\tilde{\beta}} required in (19) and used in the convex subproblems (20) and (21).}

\resp We thank the reviewer for the comment. We have included additional material on how to choose the operating point while initializing the iterative algorithm. It is described briefly in the fourth paragraph following (23). We have also provided a detailed discussion on how to update the operating point after each iteration in the paragraphs following (23). Since the objective function is convex, we can update the current operating point with the solution obtained from the previous iteration as
\begin{equation}
\tilde{\mbf{m}}_{j}^{(i)} = \mvec{m}{j}^{(i)}
\end{equation}
where \eqn{\mbf{m} = \{\mbf{m}_{l,k,n} \}_{\forall l, \forall k \in \mc{U}, \forall n}} corresponds to the collection of all transmit precoders in the system. Note that \eqn{\tilde{\mbf{m}}_{j}^{(i)}} is the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step and \eqn{\mbf{m}_{j}^{(i)}} is the solution obtained by solving (20) in the \eqn{\ith{j}} \ac{SCA} iteration.

### 2015-07-30 Report/wsrm_formulation.tex
Updated with proper response

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}. Let \eqn{\mbf{m},\mbf{w}}, and \eqn{\mbfa{\beta}} denote the corresponding sets obtained by grouping all transmit precoders, receive beamformers and interference values respectively in the system. Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step. In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is updated as \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\ast}, \mbfa{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq K_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr} and increment $j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}

>>>>

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}. For brevity, let us consider \eqn{\mbf{m}} as the collection of all transmit precoders in the system as \eqn{\mbf{m} = \{\mvec{m}{l,k,n}\}_{\forall l,\forall k, \forall n}}. Similarly, we denote \eqn{\mbf{w}} and \eqn{\mbfa{\beta}} as \eqn{\{\mvec{w}{l,k,n}\}_{\forall l,\forall k, \forall n}} and \eqn{\{\mvec{\beta}{l,k,n}\}_{\forall l,\forall k, \forall n}} respectively. Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution of \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step. Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\ast}, \mbfa{\beta}^{(i)}_{j} \}}. Note that \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver, which is obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq K_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr} and increment $j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}
